---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vlindersRarefaction

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/PietrH/vlindersRarefaction/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/PietrH/vlindersRarefaction/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/PietrH/vlindersRarefaction/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/PietrH/vlindersRarefaction/actions/workflows/test-coverage.yaml)
<!-- badges: end -->



## Installation

You can install the development version of vlindersRarefaction from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PietrH/vlindersRarefaction")
```

## Scope

This simple and experimental package converts a dataframe with a known format to 
the format the [iNEXT package](https://github.com/AnneChao/iNEXT) expects for abundance and incidence frequency data. 

The package was written with exactly this file in mind as a draft, with little 
flexibility. This means that if your file doesn't look like this:

```{r echo=FALSE}
data(warande)
dplyr::glimpse(warande)
```

This package will not work for you. Please create an issue if you would like to 
use it on data of a different shape (although at that point I'll probably just 
rewrite it to accept DarwinCore occurrence inputs).

This is a basic example on how you can plug this package into iNEXT:

```{r example, echo=TRUE}
library(vlindersRarefaction)

## convert to formats iNEXT is expecting, then calculate rarefaction curves
rare_out_inc <-
  iNEXT::iNEXT(convert_to_incidence_freq(warande),
               datatype = "incidence_freq",
               nboot = 2 # for speed
               )
rare_out_abun <-
  iNEXT::iNEXT(convert_to_abundance(warande),
               datatype = "abundance",
               nboot = 2 # for speed
               )
## and plot them:
iNEXT::ggiNEXT(rare_out_abun) + ggplot2::ggtitle("Abundance based")
iNEXT::ggiNEXT(rare_out_inc) + ggplot2::ggtitle("Incidence based")

```
