---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vlindersRarefaction

<!-- badges: start -->

[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/PietrH/vlindersRarefaction/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/PietrH/vlindersRarefaction/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/PietrH/vlindersRarefaction/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/PietrH/vlindersRarefaction/actions/workflows/test-coverage.yaml)
[![Codecov test
coverage](https://codecov.io/gh/PietrH/vlindersRarefaction/branch/main/graph/badge.svg)](https://app.codecov.io/gh/PietrH/vlindersRarefaction?branch=main)

<!-- badges: end -->

## Installation

You can install the development version of vlindersRarefaction from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PietrH/vlindersRarefaction")
```

## Scope

This simple and experimental package converts a dataframe with a known
format to the format the [iNEXT
package](https://github.com/AnneChao/iNEXT) expects for abundance and
incidence frequency data.

The package was written with exactly this file in mind as a draft, with
little flexibility. This means that your file will need the following
columns as a minimum:

-   date
-   species_name
-   year
-   number

Any number of extra columns can be provided to split the rarefaction on,
these are called *assemblages* in the context of iNEXT.

```{r echo=FALSE}
data(warande)
dplyr::glimpse(warande)
```

This is a basic example on how you can plug this package into iNEXT:

```{r example, echo=TRUE}
library(vlindersRarefaction)

## convert to formats iNEXT is expecting, then calculate rarefaction curves
rare_out_inc <-
  iNEXT::iNEXT(convert_to_incidence_freq(warande),
               datatype = "incidence_freq",
               nboot = 2 # for speed
               )
rare_out_abun <-
  iNEXT::iNEXT(convert_to_abundance(warande),
               datatype = "abundance",
               nboot = 2 # for speed
               )
## and plot them:
iNEXT::ggiNEXT(rare_out_abun) + ggplot2::ggtitle("Abundance based")
iNEXT::ggiNEXT(rare_out_inc) + ggplot2::ggtitle("Incidence based")

```
Now with an assemblage set:

```{r example-with-assemblage, echo=TRUE}

# Let's generate some random area's for the observations to belong to.
warande_gebieden <- warande %>% 
  dplyr::mutate(gebied =
                  sample(
                    c("gebied_a", "gebied_b"),
                    nrow(warande),
                    replace = TRUE)
  )

rare_out_inc_gebied <-
  iNEXT::iNEXT(convert_to_incidence_freq(warande_gebieden, gebied),
               datatype = "incidence_freq",
               nboot = 2 # for speed
               )

rare_out_abun_micromacro <- 
    iNEXT::iNEXT(convert_to_abundance(warande, MicroMacro),
               datatype = "abundance",
               nboot = 2 # for speed
               )

## and plot them:
iNEXT::ggiNEXT(rare_out_inc_gebied) + ggplot2::ggtitle("Incidence based, with areas")
iNEXT::ggiNEXT(rare_out_abun_micromacro) + ggplot2::ggtitle("Abundance based, split on Micro/Macro")
```

