---
title: "plotting-warande"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plotting-warande}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vlindersRarefaction)
```

```{r read input data}
warande <- readr::read_delim("../tblWarandepark.csv", delim = ";")
```
## Incidence based rarefaction curve

Splitting it up in `Micro` and `Macro`

### Getting the data in the right shape

iNEXT expects incidence data to consist of a list of frequencies, with the first element of the list the number of sampling units, followed by the incidence frequencies. The length of the list should be the number of observed species minus one. 

This package provides a function to convert a dataframe with a known shape (and
exactly this shape) to this format. 

```{r demo convert_to_incidence_freq, include=FALSE}
convert_to_incidence_freq(warande)
  
```



```{r calculate rarefaction by incidence}
rare_out_inc <- 
  iNEXT::iNEXT(
    convert_to_incidence_freq(warande),
    datatype = "incidence_freq",
    nboot = 50 # you might want to set this a bit higher
    )

rare_out_inc
```

And plot it:

```{r plot incidence based curve}
iNEXT::ggiNEXT(rare_out_inc)
```

## Abundance based

Splitting it up in `Micro` and `Macro`

### Getting the data in the right shape

```{r}
abundance_data <- 
  warande %>% 
    dplyr::group_by(MicroMacro) %>% 
    dplyr::count(species_name) %>% 
    dplyr::group_split() %>% 
    purrr::map(~dplyr::pull(.x, n)) %>% 
    purrr::set_names(c("Macro", "Micro"))
```
Plug this into iNEXT:

```{r}
rare_out_abun <- 
  iNEXT::iNEXT(abundance_data,
             datatype = "abundance",
             nboot = 500)
rare_out_abun

```
And plot it:

```{r}
iNEXT::ggiNEXT(rare_out_abun)
```

