---
title: "Basic plotting of rarefaction curves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plotting-warande}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Creating some rarefaction curves for butteryfly data
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vlindersRarefaction)
```

```{r read input data}
data(warande) # example data included in package
dplyr::glimpse(warande)
```
## Incidence based rarefaction curve

Splitting it up in `Micro` and `Macro`

### Getting the data in the right shape

iNEXT expects incidence data to consist of a list of frequencies, with the first element of the list the number of sampling units, followed by the incidence frequencies. The length of the list should be the number of observed species minus one. 

This package provides a function to convert a dataframe with a known shape (and
exactly this shape) to this format. 

You can provide a column that will be used to split your dataframe into assemblages.

```{r demo convert_to_incidence_freq, include=FALSE}
convert_to_incidence_freq(warande)
  
```

Let's set our assemblage to MicroMacro, so have one assembly for the Micro butterflies, and one for the Macro butterflies.

```{r calculate rarefaction by incidence}
rare_out_inc <- 
  iNEXT::iNEXT(
    convert_to_incidence_freq(warande, assemblage = MicroMacro),
    datatype = "incidence_freq",
    nboot = 50 # you might want to set this a bit higher
    )

rare_out_inc
```

And plot it:

```{r plot incidence based curve}
iNEXT::ggiNEXT(rare_out_inc)
```

## Abundance based

Splitting it up in `Micro` and `Macro`

### Getting the data in the right shape

```{r demo convert_to_abundance, include=FALSE}
convert_to_abundance(warande)
```
Plug this into iNEXT:

```{r calculate rarefaction by abundance}
rare_out_abun <- 
  iNEXT::iNEXT(convert_to_abundance(warande, assemblage = MicroMacro),
             datatype = "abundance",
             nboot = 50 # you might want to set this a bit higher
             )
rare_out_abun

```
And plot it:

```{r plot abundance based curve}
iNEXT::ggiNEXT(rare_out_abun)
```

