---
title: "Plotting data from a waarnemingen.be export"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plotting-waarnemingen-data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vlindersRarefaction)
```

Reading some data from waarnemingen.be

```{r read-data}
data("waarnemingen_dirk")
dplyr::glimpse(waarnemingen_dirk)
```

We only need a few of these columns, let's demonstrate by plotting rarefaction curves for the families in this dataset, for the two locations in the dataset.

First get rid of any rows with missing data. Let's only keep columns we are going to use, and add a year column. Let's also remove any families with less than 100 individuals observed

```{r cleanup}

families_to_plot <- 
  waarnemingen_dirk %>% 
  dplyr::group_by(family) %>% 
  dplyr::summarise(n_individuals_observed = sum(number)) %>% 
  dplyr::filter(n_individuals_observed >= 100) %>% 
  dplyr::pull(family)

waarnemingen_cleaned <- 
  waarnemingen_dirk %>% 
  dplyr::select(date,
         species_name,
         family,
         number,
         location) %>% 
  dplyr::mutate(
    year = lubridate::year(date)
  ) %>% 
  dplyr::filter(!is.na(family),
                !is.na(location),
                family %in% families_to_plot)
```

Let's group by location, and then create some plots:



```{r}
waarnemingen_grouped_by_location <-
  dplyr::group_by(waarnemingen_cleaned, location)

area_names <- 
    dplyr::group_keys(waarnemingen_grouped_by_location) %>% 
    dplyr::pull(1)

 waarnemingen_grouped_by_location %>% 
  dplyr::group_map(
      ~convert_to_abundance(.x, family)
  ) %>% 
  purrr::map(~iNEXT::iNEXT(.x,
                           datatype = "abundance",
                           nboot = 50,
                           endpoint = 1000)) %>% 
  purrr::map2(area_names,~iNEXT::ggiNEXT(.x) + ggplot2::ggtitle(.y))
```

